% NOTE: This is very inspired by http://www.toofishes.net/blog/latex-resume-follow-up/

\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[stretch=10]{microtype}
\usepackage{hyperref}
\usepackage{tgpagella}
\usepackage{enumitem}
\usepackage{indentfirst}
\pagestyle{empty}

\begin{document}

\begin{center}
{\huge \textbf{Zameer Manji}}

% NOTE: Alternatively could have used \hfill

\href{http://www.github.com/zmanji/}{www.github.com/zmanji}\ \ \textbullet
\ \ \href{http://www.zameermanji.com}{http://www.zameermanji.com}\ \ \textbullet
\ \ \href{malto:resume@zameermanji.com}{resume@zameermanji.com}

\end{center}

\hrule
\vspace{-1.0em}
\subsection*{About Me}
\indent I'm seeking a Software Engineering position involving backend systems. I
give a preference to positions which leverage my background in cluster
scheduling and container management with \href{aurora.apache.org}{Apache Aurora}
and \href{mesos.apache.org}{Apache Mesos}.

I'm passionate about immutable, reliable, automated infrastructure that scales
with technical and organizational needs.
\\

\hrule
\vspace{-1.0em}
\subsection*{Work Experience}
  \begin{itemize}
    \parskip=-0.5em

    % Twitter Promotion
    \item[]
    {\href{http://www.twitter.com}{\textbf{Twitter}} \hfill
      \textbf{San Francisco, CA}}
    \\
    {\emph{Software Engineer II} \hfill \emph{September 2015 - Present}}

    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Contributed to internal deploy system to allow users to deploy to
        multiple \href{aurora.apache.org}{Apache Aurora} zones.
      \item Independently worked on reducing technical debt on task specific
        observability tooling.
      \item Independently worked with many engineers at Twitter to improve
        internal Python build hygiene.
    \end{itemize}


    % Twitter FT
    \item[]
    {\href{http://www.twitter.com}{\textbf{Twitter}} \hfill
      \textbf{San Francisco, CA}}
    \\
    {\emph{Software Engineer I} \hfill \emph{August 2014 - August 2015}}

    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Contributed usability fixes to the
        \href{aurora.apache.org}{Apache Aurora} command line client.
      \item Created an analytics pipeline to gain better understanding of
        compute cluster utilization and allocation.
      \item Worked with operators to increase overall reliability of compute
        cluster.
    \end{itemize}

    % Twitter 2.0
    \item[]
    {\href{http://www.twitter.com}{\textbf{Twitter}} \hfill
      \textbf{San Francisco, CA}}
    \\
    {\emph{Intern} \hfill \emph{September 2013 - December 2013}}

    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Improved \href{aurora.apache.org}{Apache Aurora}
        preemption system to terminate multiple low priority tasks in favor of
        high priority tasks.
      \item Improved \href{aurora.apache.org}{Apache Aurora}
        scheduling algorithm to penalize short lived tasks to reduce wasted
        scheduling attempts.
    \end{itemize}

    % Twitter
    \item[]
    {\href{http://www.twitter.com}{\textbf{Twitter}} \hfill
      \textbf{San Francisco, CA}}
    \\
    {\emph{Intern} \hfill \emph{January 2013 - April 2013}}

    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Designed and implemented a stream filtering system on top of Apache
        Kafka to reduce stream size.
      \item Created a DSL for operators to filter streams of arbitrary Thrift
        messages.
    \end{itemize}

    % DISQUS
    \item[]
    {\href{http://www.disqus.com}{\textbf{DISQUS}} \hfill
      \textbf{San Francisco, CA}}
    \\
    {\emph{Intern} \hfill \emph{May 2012 - August 2012}}

    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Worked on performance measurement tools to catch regressions before
        systems were deployed.
      % \item Worked on performance measurement tools forming the basis for the
      %       open source projects:
      %       \href{https://github.com/disqus/nose-performance}{\textit{nose-performance}}
      %       and \href{https://github.com/disqus/zumanji}{\textit{Zumanji}}.
      % \item Independently integrated code review and testing servers to test
      %       patches before they were committed.
    \end{itemize}


    % TWG
    \item[]
    {\href{http://www.twg.ca}{\textbf{The Working Group}} \hfill
      \textbf{Toronto, ON}}
    \\
    {\emph{Software Developer} \hfill \emph{September 2011 - December 2011}}

    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Full stack work using Ruby on Rails and JavaScript projects for various
        clients.
    \end{itemize}

    % Xtreme
    \item[]
    {\href{http://www.xtremelabs.com/}{\textbf{Xtreme Labs}} \hfill
      \textbf{Toronto, ON}}
    \\
    {\emph{Agile Engineer} \hfill \emph{January 2011 - April 2011}}

    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Full stack work using Ruby on Rails and JavaScript for an OpenX
        based mobile ad network.
    \end{itemize}

    % Trapeze
    \item[]
    {\href{http://www.trapezegroup.com/}{\textbf{Trapeze Group}} \hfill
      \textbf{Mississauga, ON}}
    \\
    {\emph{Software Developer} \hfill \emph{May 2010 - August 2010}}

    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Improved web interface and search functionality on bus dispatch
        application for transportation agencies.
    \end{itemize}
  \end{itemize}


% TODO(zmanji): Revise this. Turn it into a 'Keywords' section?
% \hrule
% \vspace{-0.4em}
% \subsection*{Technical Skills}
% \begin{description}[labelindent=\parindent]
%   \item[Languages:]
%   Assembly, C, C++, Java, JavaScript, \LaTeX, Python, Ruby (on Rails)
% \end{description}

\hrule
\vspace{-1.0em}
\subsection*{Education}
  \begin{itemize}
    \parskip=-0.5em

    \item[]
    {\href{http://www.uwaterloo.ca}{\textbf{University of Waterloo}} \hfill
      \textbf{Waterloo, ON}}
    \\
    {\emph{Bachelors of Software Engineering} \hfill
      \emph{September 2009 - June 2014}}

    \begin{itemize}[label=\textbullet]
      \item Related Coursework: Compilers, Programming Languages, Operating
        Systems, Networking, Distributed Systems.
      \item Proposed patches to eCryptfs file system to support
        integrity protecting cipher modes for design project.
      \item Created a compiler for a subset of Java 1.3 for the
        x86 architecture for compilers course.
    \end{itemize}
  \end{itemize}

\hrule
\vspace{-1.0em}
\subsection*{Keywords}
\begin{description}[labelindent=\parindent]
  \parskip=-0.5em
  \item[Languages:] Java, Python, Scala
  \item[Systems:] Apache Aurora, Apache Mesos, Docker, Private Cloud
\end{description}

\end{document}
